HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-06 paper/main.tex
abstract

@@

\title{Human accuracy evaluation using UCCA}

@@

\begin{abstract}
 This document contains instructions for preparing ACL 2016 submissions and camera-ready
  manuscripts.  The document itself conforms
  to its own specifications, and is therefore an example of what
  your manuscript should look like.  Papers are required to conform to
  all the directions reported in this document.  
By using the provided \LaTeX\ and \BibTeX\ styles ({\small\tt acl2016.sty}, {\small\tt acl2016.bst}), the required formatting will be enabled by default.
\end{abstract}

\section{ Human Semantic Evaluation}
\label{sec:sem-eval:human}
We focus on producing high accuracy machine translation systems, but common 
automatic MT metrics are not able to directly capture accuracy. Even previously suggested methods
for using humans to evaluate accuracy are highly problematic. We aim to  develop a human evaluation method 
which is reliable and affordable and apply it to the MT prototypes. 
%This 
The
work described
in this section relates to 
%the 
task
\emph{T5.2: Human semantic evaluation}.
% defined in the description of action.

@@

\begin{figure}[ht]
    \includegraphics[width=1\textwidth]{ucca-tree}
    \caption{UCCA Tree with scenes}
    \label{ucca-tree}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=1\textwidth]{ucca-tree-mteval}
    \caption{UCCA Tree evaluated in comparison to an aligned ``translation'' (an
	English paraphrase).}
    \label{ucca-tree-mteval}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=1\textwidth]{interface-annotations}
    \caption{Machine translation evaluation tool}
    \label{mttool}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=1.1\textwidth]{tree_convert.png}
    \caption{UCCA tree on the source labelled with the MT Eval labels and aligned to the target translation. The 
    ``Acceptable'' structural nodes are yellow, the ``Bad'' ones are blue.}
    \label{fig:ucca-tree-evaluated}
\end{figure}

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\oa}[1]{\footnote{\color{red} #1}}

@@

\title{HUME: Human UCCA-based Machine-Translation Evaluation}

@@

\begin{abstract}

  Semantic evaluation of Machine Translation (MT) systems has become
  a necessity, given recent interest in semantics-aware MT systems.
  We present a novel human semantic evaluation measure for MT, Human
  UCCA-based MT evaluation (HUME), building on the UCCA semantic representation scheme.
  Making progress over previous work, the proposed measure takes into account
  a wider range of semantic phenomena and does not rely on semantic annotation
  of the MT output, whose interpretation is often unclear. 
  We experiment with four language pairs, demonstrating the broad applicability of
  the measure, as well as its reliability, reflected by the inter-annotator agreement
  rates.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

Human judgement is the central (and perhaps the ultimate) criterion for the quality of an MT system.
Nevertheless, common measures for MT evaluation, such as adequacy and frequency judgements or the relative
ranking of several possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number so to reflect the quality of the entire sentence, even for a
trained annotator. This also shows up with the diminishing IAA scores as a function of the
sentence length \cite{}.
Second, a single number is not instructive enough for localizing the translation errors, so to inform
the improvement of the MT system. This problem is partly addressed by using scores that decompose over
the sub-parts of the sentence, such as BLEU, thereby localizing the translation error.
However, decomposition into n-grams are most suitable for evaluating shallow methods,
such as phrase-based translation, 
and are less instructive for more structurally-aware methods,
which are at the forefront of MT research today.

These difficulties have motivated the definition of a human measure that decomposes over the semantic
structure of the sentence, rather than its n-grams. The most notable attempt of this brand is the HMEANT
measure \cite{LoWu2010,LoWu2011a,LoWu2011b,LoWu2012}, which is based on the similarity
between the translation output and a reference, defined in terms of the verbal argument structures of the
two sentences. While appealing in addressing the two major shortcomings detailed above, HMEANT 
is unable to capture semantic differences which do not show up in the verb-argument structure,
including several very frequent phenomena, such as inter-clause linkage, nominalizations and copula clauses
(see \secref{}). For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb. 
Another problem with HMEANT is that it requires semantically annotating MT output, which is often unintelligible,
as well as involves the annotation and comparison to a reference translation: an impractical if not unattainable
solution, given the huge number of reasonable translations a sentence may have \cite{dryer_marcu:12}.

In this work we propose the Human UCCA-based MT Evaluation ({\it HUME}) metric,
a human evaluation measure that decomposes over local semantic structures.
The measure is based on a decomposition of the source sentence into semantic units according
to the UCCA semantic annotation, and the estimation of their translation quality.
UCCA covers a wide range of fundamental linguistic phenomena,
including verbal, nominal and adjectival argument structures, inter-clause relations, coorindation
and others. Importantly, HUME only requires an annotation of the source sentence, thus avoiding the 
annotatation machine-generated text. By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, but impose the additional requirement
that the evaluator be proficient in both the source
and target languages.
Further discussion of the strengths and weaknesses of HUME relative to previous approaches
can be found in \secref{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Human Semantic Evaluation}
\label{sec:sem-eval:human}
We focus on producing high accuracy machine translation systems, but common 
automatic MT metrics are not able to directly capture accuracy. Even previously suggested methods
for using humans to evaluate accuracy are highly problematic. We aim to  develop a human evaluation method 
which is reliable and affordable and apply it to the MT prototypes. 
%This 
The
work described
in this section relates to 
%the 
task
\emph{T5.2: Human semantic evaluation}.
% defined in the description of action.

@@

\begin{figure*}[t]
    \includegraphics[width=1\textwidth]{ucca-tree}
    \caption{UCCA Tree with scenes}
    \label{ucca-tree}
\end{figure*}

@@

\begin{figure*}[t]
    \includegraphics[width=1\textwidth]{ucca-tree-mteval}
    \caption{UCCA Tree evaluated in comparison to an aligned ``translation'' (an
	English paraphrase).}
    \label{ucca-tree-mteval}
\end{figure*}

@@

\begin{figure*}[t]
    \includegraphics[width=1\textwidth]{interface-annotations}
    \caption{Machine translation evaluation tool}
    \label{mttool}
\end{figure*}

@@

\begin{figure*}[t]
    \includegraphics[width=1.1\textwidth]{tree_convert.png}
    \caption{UCCA tree on the source labelled with the MT Eval labels and aligned to the target translation. The 
    ``Acceptable'' structural nodes are yellow, the ``Bad'' ones are blue.}
    \label{fig:ucca-tree-evaluated}
\end{figure*}
